Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression\thanksref{T1}

### 2020-04-13 revision_2/paper.tex
minor typos

The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood, provides context with previous work, and demonstrates some advantages of the methods on simple examples. Section~\ref{BayesLinMod} details an MCMC algorithm to apply the method to Bayesian linear models. This computational strategy is a major contribution to the work, providing an approach to apply the method on realistic examples. Many of the the technical proofs are in the Appendix \ref{sec:appendix} with \texttt{R} code available from the authors. Sections \ref{simData} and \ref{RealData} illustrate the method with simulated data and a real insurance industry data set containing many outliers with a novel twist on model evaluation. A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method. \response{ An R package \texttt{brlm} is to implement our methods in available at \texttt{github.com/jrlewi/brlm}. Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}

@@

\subsection{Practical Considerations for Using the Restricted Likelihood}
We offer the following guidelines and recommendations for using these methods in practice. 
\begin{itemize}
\item We have the method useful in outlier prone situations where good prior information can be encoded for the `good' part of the model. The additional computation burden may be too much when this is not the case. Traditional robust estimation techniques are often quicker and can provide comparable results.
\item Currently, we recommend conditioning on classical robust estimators when pursing these methods. Default choices are Huber's and Tukey's estimators as outlined in the paper. We have found default choices (e.g. obtaining 95\% efficiency under normally distributed data) for the tuning parameters to work well in many situations. However, depending on the amount of contamination, some adjustment may be necessary. 
\item The likelihood itself can indeed take many forms and, like the conditioning statistic, can depend on the application. We have developed methods for fitting these models under a large class of conditioning statistics. Currently the default choice in outlier prone situations is to use a normal likelihood model, with the conditioning intended to reduce the sensitivity of the analysis to the outliers. 
\item Comparisons amongst various choices of conditioning statistics and models can be made via standard cross-validation techniques like those done in this paper where models are fit to several training and holdout sets. One should take care in the method of evaluation. When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data ins some way (such as the trimmed-log-marginal we introduced TLM).
\end{itemize}

>>>>

The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood, provides context with previous work, and demonstrates some advantages of the methods on simple examples. Section~\ref{BayesLinMod} details an MCMC algorithm to apply the method to Bayesian linear models. This computational strategy is a major contribution to the work, providing an approach to apply the method on realistic examples. Many of the the technical proofs are in the Appendix \ref{sec:appendix} with \texttt{R} code available from the authors. Sections \ref{simData} and \ref{RealData} illustrate the method with simulated data and a real insurance industry data set containing many outliers with a novel twist on model evaluation. A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method. \response{ An R package \texttt{brlm} to implement our methods is available at \texttt{github.com/jrlewi/brlm}. Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}

@@

\subsection{Practical Considerations for Using the Restricted Likelihood}
We offer the following guidelines and recommendations for using these methods in practice. 
\begin{itemize}
\item We have the method useful in outlier prone situations where good prior information can be encoded for the `good' part of the model. The additional computation burden may be too much when this is not the case. Traditional robust estimation techniques are often quicker and can provide comparable results.
\item Currently, we recommend conditioning on classical robust estimators when using these methods. Default choices are Huber's and Tukey's estimators as outlined in the paper. We have found default choices (e.g. obtaining 95\% efficiency under normally distributed data) for the tuning parameters to work well in many situations. However, depending on the amount of contamination, some adjustment may be necessary. 
\item The likelihood itself can indeed take many forms and, like the conditioning statistic, can depend on the application. We have developed methods for fitting these models under a large class of conditioning statistics. Currently the default choice in outlier prone situations is to use a normal likelihood model, with the conditioning intended to reduce the sensitivity of the analysis to the outliers. 
\item Comparisons amongst various choices of conditioning statistics and models can be made via standard cross-validation techniques like those done in this paper where models are fit to several training and holdout sets. One should take care in the method of evaluation. When the goal is to obtain good estimation/prediction for the non-outlying data, evaluation should take place on non-outlying data or the metric should be adjusted to discount outlying data ins some way (such as the trimmed-log-marginal we introduced TLM).
\end{itemize}
